Measuring individual differences in the understanding of gaze cues

### 2022-02-23 paper/manuscript.Rmd
add the first plots for interind variation

```{r load_data}
library(tidyverse)
testtrials <- readRDS(file = "../data/gafo-testtrials.rds") %>% 
  # determine order of factors
  mutate(
    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
    studyversion = factor(studyversion, levels = c("hedge", "box")), 
    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
    sample = factor(sample, levels = c("kids", "adults")), 
    studytype = factor(studytype, levels = c("vali", "vali2", "reli"))
  )
```

@@

## Stimuli
Our newly implemented balloon finding task displays cartoon-like stimuli that are engaging for children and adults alike. An animal character (i.e., agent; sheep, monkey, or pig) is placed centrally in a window. A balloon (i.e., target; blue, green, yellow, or red) is located in front of them. The target then falls to the ground. At all times, the agent’s gaze tracks the movement of the target. That is, the pupils and iris of the agent move in a way that their center aligns with the center of the target. While the distance of the target's flight depends on the final location, the target moves at a constant speed. Participants are then asked to locate the target’s position on the screen.

@@

## Trials
Before participants advance to the test trials, we present four training trials. In the first training trial, participants have full visual access to the target flight and the target's end location and are simply asked to click on the visible balloon. In the second and third training trials, participants have partial visual access: they witness the target flight but cannot see the target's end location. They are then asked to click on the invisible balloon, i.e., the location where they saw the target land. In test trials, participants have no visual access to the target flight nor the end location. Participants are expected to use the agent’s gaze as a cue to locate the target. The first trial of each type comprises a voice-over description of the presented events. The audio descriptions explicitly state that the agent is always looking at the target (see Appendix for audio script). After these four training and audio guided trials, participants receive 15 test trials. The complete sequence of four training trials and 15 test trials can be administered within 5-10 minutes of testing time.

@@

## Implementation
Our balloon finding task is presented as an interactive web-app. The task is portable across devices and web browsers and does not require any installation. A great advantage of online testing is that our testing procedure is standardized across participants. By using pre-recorded study instructions,no interaction with the experimenter is necessary during the study. The code is open-source (https://github.com/ccp-eva/gafo-demo) and a live demo version can be found under: https://ccp-odc.eva.mpg.de/gafo-demo/.

@@

The web-app generates two file types: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
For our samples described in this paper, we deployed the web-app on servers located in Leipzig, Germany. Data got automatically collected and safely stored on these in-house servers. If no internet connection or server is available, researchers could download a local version of the experiment which stores the generated data automatically on the used device.

(ref:figlab2) **Infrastructure for online testing**. With our new infrastructure, subjects aged 3 – 99+ can participate. Data collection is efficient and automatized and can take place anywhere: at home, in kindergartens or research institutes. Our task is presented as a website that works across devices. The scripts for the website and recorded data are stored on secure local servers.
```{r fig2, out.width="100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
knitr::include_graphics("../figures/infrastructure.png")
```

## Data processing
- workflow server to R, converting coordinate systems
We used `r cite_r("r-references.bib")` for all our analyses.
For child samples, we uploaded safety copies of the already collected responses after the fourth test trial. In cases where children want to stop participation earlier, no responses get lost. All test trials without voice over description are included in our analyses.

# Does the balloon finding task induce variation?
```{r vali_sample}
vali <- testtrials %>% 
  filter(studytype == "vali" & (ageInYears < 6 | ageInYears == 18))

@@

vali_adults <- vali_adults %>% 
  full_join(vali_adults_gender, by = character())
```
## Participants
Our first aim was to assess whether our balloon finding task induces variation in a child and adult sample. The pre-registrations can be found here: https://osf.io/snju6 (child sample) and here: https://osf.io/r3bhn (adult sample). Participants were equally distributed across the two study versions.

For our child sample, we went to kindergartens in Leipzig and surroundings that cooperate with the Max Planck Institute for Evolutionary Anthropology. Children in our sample grow up in an industrialized, urban Central-European context. Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education. 
The child sample consisted of 
`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised"])` children, including 
`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` 3-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` girls),
`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` 4-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` girls),
and `r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` 5-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` girls). 
Children received a small thank-you gift for their participation in the study.

@@

## Procedure
All participants received 15 test trials that were displayed as described above. In the box version, we decided to adjust the task difficulty according to the participant's age: children were presented with five boxes while adults were presented with eight boxes as possible hiding location of the target.

## Results
- for hedge & box
- sanity check: developmental trajectory
- remote testing: online child sample as side note

@@

# Can we capture variation reliably?
```{r reli_sample}
reli <- testtrials %>% 
  filter(studytype == "reli" & (ageInYears < 6 | ageInYears == 18) & completedReli)

@@

reli_adults <- reli_adults %>% 
  full_join(reli_adults_gender, by = character())
```
## Participants
Our second aim was to assess whether the variation that we captured with our balloon finding task is reliable. The pre-registrations can be found here: https://osf.io/xqm73 (child sample) and here: https://osf.io/nu62m (adult sample).

For our child sample, we again went to kindergartens in Leipzig and surroundings.
The child sample consisted of 
`r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised"])` children, including 
`r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])` 3-year-olds 
(mean = `r sum(reli_kids$meanAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])` months, 
SD = `r sum(reli_kids$sdAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])`, 
range = `r sum(reli_kids$minAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])`
- `r sum(reli_kids$maxAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])`, 
`r sum(reli_kids$nFemales[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])` girls),
`r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])` 4-year-olds 
(mean = `r sum(reli_kids$meanAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])` months, 
SD = `r sum(reli_kids$sdAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])`, 
range = `r sum(reli_kids$minAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])`
- `r sum(reli_kids$maxAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])`, 
`r sum(reli_kids$nFemales[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])` girls),
and `r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])` 5-year-olds 
(mean = `r sum(reli_kids$meanAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])` months, 
SD = `r sum(reli_kids$sdAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])`, 
range = `r sum(reli_kids$minAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])`
- `r sum(reli_kids$maxAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])`, 
`r sum(reli_kids$nFemales[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])` girls).

@@

# Exploring the external validity of our task
```{r peerexposure_sample}
pe <- testtrials %>% 
  filter(ageInYears < 6) %>% 
  select(datacollection, studyversion, subjID, gender, trialNr, ageInMonths, ageInYears, correctBox, childcareAge, childcareHours, householdTotal, siblingsNr, siblingsChildAged, siblingsVarietyScoreP, siblingsVarietyScoreW, targetPosition, targetCentralityX) %>% 
  # so that all models run with same nr of subjects
  drop_na()

@@

## Participants
Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social surroundings. For this exploratory analysis, we included all children of the aforementioned samples where families filled out a short demographic questionnaire. Our sample consisted of 
`r sum(pe_sample$nTotal)` children, including 
`r sum(pe_sample$nTotal[pe_sample$ageInYears == "3"])` 3-year-olds 
(mean = `r sum(pe_sample$meanAgeInMonths[pe_sample$ageInYears == "3"])` months, 
SD = `r sum(pe_sample$sdAgeInMonths[pe_sample$ageInYears == "3"])`, 
range = `r sum(pe_sample$minAgeInMonths[pe_sample$ageInYears == "3"])`
- `r sum(pe_sample$maxAgeInMonths[pe_sample$ageInYears == "3"])`, 
`r sum(pe_sample$nFemales[pe_sample$ageInYears == "3"])` girls),
`r sum(pe_sample$nTotal[pe_sample$ageInYears == "4"])` 4-year-olds 
(mean = `r sum(pe_sample$meanAgeInMonths[pe_sample$ageInYears == "4"])` months, 
SD = `r sum(pe_sample$sdAgeInMonths[pe_sample$ageInYears == "4"])`, 
range = `r sum(pe_sample$minAgeInMonths[pe_sample$ageInYears == "4"])`
- `r sum(pe_sample$maxAgeInMonths[pe_sample$ageInYears == "4"])`, 
`r sum(pe_sample$nFemales[pe_sample$ageInYears == "4"])` girls),
and `r sum(pe_sample$nTotal[pe_sample$ageInYears == "5"])` 5-year-olds 
(mean = `r sum(pe_sample$meanAgeInMonths[pe_sample$ageInYears == "5"])` months, 
SD = `r sum(pe_sample$sdAgeInMonths[pe_sample$ageInYears == "5"])`, 
range = `r sum(pe_sample$minAgeInMonths[pe_sample$ageInYears == "5"])`
- `r sum(pe_sample$maxAgeInMonths[pe_sample$ageInYears == "5"])`, 
`r sum(pe_sample$nFemales[pe_sample$ageInYears == "5"])` girls).

>>>>

```{r load_data}
library(tidyverse)
library(brms)
testtrials <- readRDS(file = "../data/gafo-testtrials.rds") %>% 
  # determine order of factors
  mutate(
    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
    studyversion = factor(studyversion, levels = c("hedge", "box")), 
    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
    sample = factor(sample, levels = c("kids", "adults")), 
    studytype = factor(studytype, levels = c("vali", "vali2", "reli"))
  )
```

@@

## Stimuli
Our newly implemented balloon finding task displays cartoon-like stimuli that are engaging for children and adults alike. An animal character (i.e., agent; sheep, monkey, or pig) is placed centrally in a window. A balloon (i.e., target; blue, green, yellow, or red) is located in front of them. The target then falls to the ground. At all times, the agent’s gaze tracks the movement of the target. That is, the pupils and iris of the agent move in a way that their center aligns with the center of the target. While the distance of the target's flight depends on the final location, the target moves at a constant speed. Participants are then asked to locate the target’s destination: they respond by touching or clicking onto position on the screen.

@@

## Trials
Before the test trials start, we present four training trials during which participants familiarize themselves with selection positions on the screen. In the first training trial, participants have full visual access to the target flight and the target's end location and are simply asked to click on the visible balloon. In the second and third training trials, participants have partial visual access: they witness the target flight but cannot see the target's end location. They are then asked to click on the invisible balloon, i.e., the location where they saw the target land. In test trials, participants have no visual access to the target flight nor the end location. Participants are expected to use the agent’s gaze as a cue to locate the target. The first trial of each type comprises a voice-over description of the presented events. The audio descriptions explicitly state that the agent is always looking at the target (see Appendix for audio script). After these four training and audio guided trials, participants receive 15 test trials. The complete sequence of four training trials and 15 test trials can be administered within 5-10 minutes of testing time.

@@

## Implementation
Our balloon finding task is presented as an interactive web-app. The task is portable across devices and web browsers and does not require any installation. A great advantage of online testing is that our testing procedure is standardized across participants. By using pre-recorded study instructions, no interaction with the experimenter is necessary during the study. The code is open-source (https://github.com/ccp-eva/gafo-demo) and a live demo version can be found under: https://ccp-odc.eva.mpg.de/gafo-demo/.

@@

The web-app generates two file types: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
For our samples described in this paper, we deployed the web-app on servers located in Leipzig, Germany. Data got automatically collected and safely stored on these in-house servers. If no internet connection or server is available, researchers could download a local version of the experiment which stores the generated data automatically on the used device. For child samples, we upload safety copies of the already collected responses after the fourth test trial. In cases where children want to stop participation earlier, no responses get lost.

(ref:figlab2) **Infrastructure for online testing**. (i) With our new infrastructure, subjects aged 3 – 99+ can participate. Data collection is efficient and automatized and can take place anywhere: at home, in kindergartens or research institutes. (ii) Our task is presented as a website that works across devices. (iii) The scripts for the website and recorded data are stored on secure local servers.
```{r fig2, out.width="100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
knitr::include_graphics("../figures/infrastructure.png")
```

## Data processing
We used `r cite_r("r-references.bib")` for all our analyses. Regression models were fitted as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses. 
All test trials without voice over description are included in our analyses.

# Does the balloon finding task induce variation?
Our first aim was to assess whether our balloon finding task induces variation in a child and adult sample. The pre-registrations can be found here: https://osf.io/snju6 (child sample) and here: https://osf.io/r3bhn (adult sample). Participants were equally distributed across the two study versions. The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology. Data was collected between May 2021 and XXX 2022.

```{r vali_sample}
vali <- testtrials %>% 
  filter(studytype == "vali" & (ageInYears < 6 | ageInYears == 18))

@@

vali_adults <- vali_adults %>% 
  full_join(vali_adults_gender, by = character())
```
## Participants
For our child sample, we went to kindergartens in Leipzig and surroundings that cooperate with the Max Planck Institute for Evolutionary Anthropology. Children in our sample grow up in an industrialized, urban Central-European context. Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education. 
The child sample consisted of 
`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised"])` children, including 
`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` 3-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` girls),
`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` 4-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` girls),
and `r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` 5-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` girls). 
Children received a small thank-you gift for their participation in the study.

@@

## Procedure
Children were tested in a quiet room in their daycare. An experimenter guided the child through the different parts of the study.
All participants received 15 test trials that were displayed as described above. In the box version, we decided to adjust the task difficulty according to the participant's age: children were presented with five boxes while adults were presented with eight boxes as possible hiding location of the target.

## Results
- sanity check: developmental trajectory
- remote testing: online child sample as side note

We captured a developmental trajectory of gaze cue understanding. With increasing age, participants get more and more accurate in their performance.

(ref:figlab3) **Interindividual variation**. 
The regression line shows the developmental trajectory (with 95% CI) of children's performance by age. 
Colored diamonds show means by age in years (with 95% CI based on non-parametric bootstrap). Light shapes show the mean performance for each subject.
(a) Variation in the hedge version. Here, we measure performance as the average imprecision, i.e., the absolute click distance between the target's center and the participant's click. The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center. 
(b) Variation in the box version. Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target. The straight line shows level of performance expected by chance for the child sample (20%, i.e., 1 out of 5 boxes). Dotted line shows level of performance expected by chance for the adult sample (12.5%, i.e., 1 out of 8 boxes).

```{r fig3, fig.show = "hold", out.width = "49%", fig.align = "default", fig.cap = "(ref:figlab3)"}
# {r, echo=FALSE, out.width="49%", out.height="20%", fig.cap="figlab1", fig.show='hold', fig.align='center'}
knitr::include_graphics(c("../figures/gafo_hedge_variation.png", "../figures/gafo_box_variation.png"))
```

TODO: For investigating the internal consistency of our task, we split the test trials into halves...

(ref:figlab4) **Internal consistency**. 
```{r fig4, fig.show = "hold", out.width = "49%", fig.align = "default", fig.cap = "(ref:figlab4)"}
# knitr::include_graphics(c("../figures/gafo_hedge_variation.png", "../figures/gafo_box_variation.png"))
```

@@

(ref:figlab5) **Comparing data collection modes**.

```{r fig5, fig.show = "hold", out.width = "49%", fig.align = "default", fig.cap = "(ref:figlab5)"}
# knitr::include_graphics(c("../figures/gafo_hedge_variation.png", "../figures/gafo_box_variation.png"))
```

## Discussion
Study 1 showed that our newly implemented balloon finding task can be used to study gaze cue understanding in both children and adults. With increasing age, participants got more and more precise in locating the target. We found inter-individual variation in across all age groups: some three-year-olds were more precise than some five-year-olds. Internal consistency indicated that the measured variation was systematic. These results hold for both the continuous hedge version as well as the discrete box version of the task. Furthermore, we found comparable results for an unsupervised remote child sample. This underlines how flexibly our new task can be used.

# Can we capture variation reliably?
Based on the results of Study 1, we wanted to further investigate whether the variation that we captured with our balloon finding task is reliable. For this aim, we assessed the test-retest reliability by testing the same individual twice. The pre-registrations can be found here: https://osf.io/xqm73 (child sample) and here: https://osf.io/nu62m (adult sample). Participants were equally distributed across the two study versions. The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology. Data was collected between XXX 2021 and XXX 2022.

```{r reli_sample}
reli <- testtrials %>% 
  filter(studytype == "reli" & (ageInYears < 6 | ageInYears == 18) & completedReli)

@@

reli_adults <- reli_adults %>% 
  full_join(reli_adults_gender, by = character())
```
## Participants
For our child sample, we again went to kindergartens in Leipzig and surroundings.
The child sample consisted of 
`r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised"])` children, including 
`r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])` 3-year-olds 
(mean = `r sum(reli_kids$meanAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])` months, 
SD = `r sum(reli_kids$sdAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])`, 
range = `r sum(reli_kids$minAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])`
- `r sum(reli_kids$maxAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])`, 
`r sum(reli_kids$nFemales[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])` girls),
`r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])` 4-year-olds 
(mean = `r sum(reli_kids$meanAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])` months, 
SD = `r sum(reli_kids$sdAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])`, 
range = `r sum(reli_kids$minAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])`
- `r sum(reli_kids$maxAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])`, 
`r sum(reli_kids$nFemales[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])` girls),
and `r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])` 5-year-olds 
(mean = `r sum(reli_kids$meanAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])` months, 
SD = `r sum(reli_kids$sdAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])`, 
range = `r sum(reli_kids$minAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])`
- `r sum(reli_kids$maxAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])`, 
`r sum(reli_kids$nFemales[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])` girls).

@@

# Exploring the external validity of our task
Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social surroundings. 
```{r peerexposure_sample}
pe <- testtrials %>% 
  filter(ageInYears < 6) %>% 
  select(datacollection, studyversion, subjID, gender, trialNr, ageInMonths, ageInYears, correctBox, childcareAge, childcareHours, householdTotal, siblingsNr, siblingsChildAged, siblingsVarietyScoreP, siblingsVarietyScoreW, targetPosition, targetCentralityX) %>% 
  # so that all models run with same nr of subjects
  drop_na()

@@

## Participants
For this exploratory analysis, we included all children of the aforementioned samples where families filled out a short demographic questionnaire. Our sample consisted of 
`r sum(pe_sample$nTotal)` children, including 
`r sum(pe_sample$nTotal[pe_sample$ageInYears == "3"])` 3-year-olds 
(mean = `r sum(pe_sample$meanAgeInMonths[pe_sample$ageInYears == "3"])` months, 
SD = `r sum(pe_sample$sdAgeInMonths[pe_sample$ageInYears == "3"])`, 
range = `r sum(pe_sample$minAgeInMonths[pe_sample$ageInYears == "3"])`
- `r sum(pe_sample$maxAgeInMonths[pe_sample$ageInYears == "3"])`, 
`r sum(pe_sample$nFemales[pe_sample$ageInYears == "3"])` girls),
`r sum(pe_sample$nTotal[pe_sample$ageInYears == "4"])` 4-year-olds 
(mean = `r sum(pe_sample$meanAgeInMonths[pe_sample$ageInYears == "4"])` months, 
SD = `r sum(pe_sample$sdAgeInMonths[pe_sample$ageInYears == "4"])`, 
range = `r sum(pe_sample$minAgeInMonths[pe_sample$ageInYears == "4"])`
- `r sum(pe_sample$maxAgeInMonths[pe_sample$ageInYears == "4"])`, 
`r sum(pe_sample$nFemales[pe_sample$ageInYears == "4"])` girls),
and `r sum(pe_sample$nTotal[pe_sample$ageInYears == "5"])` 5-year-olds 
(mean = `r sum(pe_sample$meanAgeInMonths[pe_sample$ageInYears == "5"])` months, 
SD = `r sum(pe_sample$sdAgeInMonths[pe_sample$ageInYears == "5"])`, 
range = `r sum(pe_sample$minAgeInMonths[pe_sample$ageInYears == "5"])`
- `r sum(pe_sample$maxAgeInMonths[pe_sample$ageInYears == "5"])`, 
`r sum(pe_sample$nFemales[pe_sample$ageInYears == "5"])` girls).
